Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-09 article.tex
Part 1 is nice
Watermark artificial data
Only MHC-I for now

\begin{figure}[!htbp]
  \includegraphics[width=0.4\textwidth]{ks/fig_1.png}
  \caption{
    Condition of a Kolmogorov-Smirnov (KS) statistic to rejects a null
    hypothesis. $D_{n,m}$ is the KS statistic, $n = m$ is the size
    of the samples, in this case, the number of HLA haplotypes ($n = m = 13$).
    $\alpha = 0.05$ is the significance level.
  }
  \label{fig:ks}
\end{figure}

@@

@@

We conclude that MHC-II binds to TMH peptides with a higher/lower/equal
probability than expected by chance.

We conclude that the evolutionary conservation if the TMH parts of membrane
proteins is higher/less/equal compare to its non-TMH counterparts.

@@

We compared the mutation rates between the TMH and non-TMH part of
multiple mycoplasma species. Where we expect no variation 
in mutation rate for every TMH amino acid,
\richel{
  we can test this, but unsure if that would make sense
}
we know that non-TMH part will have regions of different evolutionary
conservation: functional domains, especially in protein-protein
interactions will be strongly conserved, due to an even more constrained
set of peptides that enable a certain function.

\richel{
  Note that most bacteria are opportunistic pathogens.
  Note that most bacteria are generalists.
  Note that most bacteria have different cell membranes (and walls), that
  may have different functional constraints than a human cell membrane
}

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=0.4\textwidth]{pics/ks.png}
  \caption{
    Condition of a Kolmogorov-Smirnov (KS) statistic to rejects a null
    hypothesis. $D_{n,m}$ is the KS statistic, $n = m$ is the size
    of the samples, in this case, the number of HLA haplotypes ($n = m = 13$).
    $\alpha = 0.05$ is the significance level.
  }
  \label{fig:ks}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ks/fig_1_watermarked.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human and COVID-19 proteome
  }
  \label{fig:1}
\end{figure}

@@

\iffalse
	We conclude that MHC-II binds to TMH peptides with a higher/lower/equal
	probability than expected by chance.

	We conclude that the evolutionary conservation if the TMH parts of membrane
	proteins is higher/less/equal compare to its non-TMH counterparts.
\fi

@@

\iffalse
	We compared the mutation rates between the TMH and non-TMH part of
	multiple mycoplasma species. Where we expect no variation 
	in mutation rate for every TMH amino acid,
	\richel{
	  we can test this, but unsure if that would make sense
	}
	we know that non-TMH part will have regions of different evolutionary
	conservation: functional domains, especially in protein-protein
	interactions will be strongly conserved, due to an even more constrained
	set of peptides that enable a certain function.

	\richel{
	  Note that most bacteria are opportunistic pathogens.
	  Note that most bacteria are generalists.
	  Note that most bacteria have different cell membranes (and walls), that
	  may have different functional constraints than a human cell membrane
	}
\fi
